Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: grammar

\begin{itemize}
	\item Model fitting times increase.
	\item Noise is possibly introduced into models by highly-correlated variables\cite{johnstoneiainm.2009}.
	\item Model interpretation and prediction tasks become more challenging\cite{johnstoneiainm.2009}.
\end{itemize}

\noindent In the following sections a brief overview about sub-categories of feature selection approaches is given.
Due to the focus of this study on the use of filter methods, which are a sub-group of feature selection methods, other approaches were grouped into a single section.

>>>>

\begin{itemize}
	\item Model fitting times increase.
	\item Noise is possibly introduced into models by highly-correlated variables\cite{johnstoneiainm.2009}.
	\item Model interpretation and prediction become more challenging\cite{johnstoneiainm.2009}.
\end{itemize}

\noindent In the following sections a brief overview of feature selection sub-categories is given.
Due to the focus of this study on the use of filter methods, which are a sub-group of feature selection methods, other approaches were grouped into a single section.
